---
title       : Estimator for MPG
subtitle    : Application for calculating the estimated miles per gallon
author      : Lena Stevanoska
job         : 
framework   : io2012   # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : solarized_light      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- bg:snow

## Why "Estimator for MPG"?



1. Let's you know what you can expect from your car
2. Just 3 simple parameters required
3. Intuitive interface

---  bg:snow

## Scientific support

Estimated value is calculated using the following formula

 $Y = \hat \beta_0 + \hat \beta_1 * X_1 + \hat \beta_2 * X_2 + \hat \beta_3 * X_3$

The $\hat \beta_k$ values are calculated using the linear regression model fitted through the mtcars dataset.

```{r model,echo=FALSE}
  fit<-lm(mpg~factor(am)+wt+cyl,data=mtcars)
	coeffit<-summary(fit)$coef
	coeffit
```
The $X_k$ values are the entered values:
* $X_1$ = Transmission type (0 = Automatic, 1 = Manual)
* $X_2$ = Weight (in $lb/1000$)
* $X_3$ = Number of cylinders (4, 6, 8)


---bg:snow


## The data used to create the prediction model

```{r loadlib,echo=FALSE,results='hide',message=FALSE,warning=FALSE}
library(ggplot2)
library(datasets)

```

```{r plotwtcyl, echo=FALSE,fig.align='center',fig.height=7,fig.width=11}
df<-data.frame(mtcars,amcyl=factor(paste(mtcars$am,mtcars$cyl,sep=".")))
g<-ggplot(df,aes(y=mpg, x=wt,fill="blue"))+geom_boxplot()+facet_wrap( ~ amcyl,ncol=6)+ylab("MPG")+xlab("Weight")
g<-g+theme_bw()+theme(legend.position="none")+ggtitle("MPG depending of the car weight (grouped by Transmission type.Number of cylinders) ")
g

```


---bg:snow

## Estimator MPG - Live demo

<iframe src='https://lsdev.shinyapps.io/EstimateMPGApp' height='600px'></iframe>
